On the combination of Set Functions and Failures

### 2013-02-13 docs/src/manual.tex
Release notes and manual updated

@@

test3 = assertSolutions "prefix" (\x -> let y free in  x++y =:= [1,2])
                                 [[],[1],[1,2]]

\end{curry}
For instance, \code{test1} asserts that the result of evaluating the
expression \code{([1,2]++[3,4])} is equal to \code{[1,2,3,4]}.

>>>>

It is also possible to combine functional patterns with
as-patterns.\index{as-pattern}\pindex{"@}
Similarly to the meaning of as-patterns
in standard constructor patterns,
as-patterns in functional patterns are interpreted
as a sequence of pattern matching where the variable of the as-pattern
is matched before the given pattern is matched.
This process can be described by introducing an auxiliary operation
for this two-level pattern matching process.
For instance, the definition
\begin{curry}
f (_ ++ x@[(42,_)] ++ _) = x
\end{curry}
is considered as syntactic sugar for the expanded definition
\begin{curry}
f (_ ++ x ++ _) = f' x
 where
  f' [(42,_)] = x
\end{curry}
However, as-patterns are usually implemented
in a more efficient way without introducing auxiliary operations.

@@

test3 = assertSolutions "prefix" (\x -> let y free in  x++y =:= [1,2])
                                 [[],[1],[1,2]]
\end{curry}
For instance, \code{test1} asserts that the result of evaluating the
expression \code{([1,2]++[3,4])} is equal to \code{[1,2,3,4]}.
